Population structure and phenotypic variation of \emph{Sclerotinia sclerotiorum} from dry bean (\emph{Phaseolus vulgaris}) in the United States

### 2017-11-13 doc/manuscript/manuscript.Rmd
fix typo that clobbered COI
fix embarassing mis-spelling

The authors would like to thank Rebecca Higgens for technical support in generating the data for the MCG assessment, aggressiveness ratings, and genotyping; and for providing valuable insights into the historical context of the data collection and curation.

We would also like to thank Denita Hadziabdic and two other anonymous reviewers for their valuable comments and insights that improved the quality of the manuscript.
## Conflicts of Interest {-}

@@

 - **James Steadman** Conceived and designed experiments, organized network of white mold screening nurseries, provided *S. sclerotiorum* isolates, edited and reviewed drafts of the paper.

@@

![
Example of MCG test plates showing (A) a compatible reaction with mycelia from two strains overgrowing each other and (B) an incompatible reaction with a barrage line of dead tissue forming between the two strains. Photo Credit: Rebecca Higgens.
](images/mcg-trimmed.png){#mcg-fig width=100%}

>>>>

The authors would like to thank Rebecca Higgins for technical support in generating the data for the MCG assessment, aggressiveness ratings, and genotyping; and for providing valuable insights into the historical context of the data collection and curation.

We would also like to thank Denita Hadziabdic and two other anonymous reviewers for their valuable comments and insights that improved the quality of the manuscript.

## Conflicts of Interest {-}

@@

 - **James R. Steadman** Conceived and designed experiments, organized network of white mold screening nurseries, provided *S. sclerotiorum* isolates, edited and reviewed drafts of the paper.

@@

![
Example of MCG test plates showing (A) a compatible reaction with mycelia from two strains overgrowing each other and (B) an incompatible reaction with a barrage line of dead tissue forming between the two strains. Photo Credit: Rebecca Higgins.
](images/mcg-trimmed.png){#mcg-fig width=100%}

### 2017-11-13 doc/manuscript/manuscript.tex
fix typo that clobbered COI
fix embarassing mis-spelling

The authors would like to thank Rebecca Higgens for technical support in
generating the data for the MCG assessment, aggressiveness ratings, and
genotyping; and for providing valuable insights into the historical
context of the data collection and curation.

We would also like to thank Denita Hadziabdic and two other anonymous
reviewers for their valuable comments and insights that improved the
quality of the manuscript. \#\# Conflicts of Interest \{-\}

@@

\begin{itemize}
\item
  \textbf{Zhian N. Kamvar} analyzed the data, contributed analysis
  tools, wrote the paper, prepared figures and tables, edited and
  reviewed drafts of the paper.
\item
  \textbf{Bimal Sajeewa Amaradasa} analyzed the data, contributed
  analysis tools, wrote drafts of the paper, edited and reviewed drafts
  of the paper.
\item
  \textbf{Rachana Jhala} Carried out experiments (MCG assessment,
  aggressiveness ratings, genotyping), edited and reviewed drafts of the
  paper.
\item
  \textbf{Serena McCoy} Carried out experiments (MCG assessment,
  aggressiveness ratings, genotyping), edited and reviewed drafts of the
  paper.
\item
  \textbf{James Steadman} Conceived and designed experiments, organized
  network of white mold screening nurseries, provided \emph{S.
  sclerotiorum} isolates, edited and reviewed drafts of the paper.
\item
  \textbf{Sydney E. Everhart} supervised data analysis, analyzed the
  data, contributed analysis tools, wrote the paper, edited and reviewed
  drafts of the paper.
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics[width=1.00000\textwidth]{images/mcg-trimmed.png}
\caption{Example of MCG test plates showing (A) a compatible reaction
with mycelia from two strains overgrowing each other and (B) an
incompatible reaction with a barrage line of dead tissue forming between
the two strains. Photo Credit: Rebecca Higgens.}\label{mcg-fig}
\end{figure}

>>>>

The authors would like to thank Rebecca Higgins for technical support in
generating the data for the MCG assessment, aggressiveness ratings, and
genotyping; and for providing valuable insights into the historical
context of the data collection and curation.

We would also like to thank Denita Hadziabdic and two other anonymous
reviewers for their valuable comments and insights that improved the
quality of the manuscript.

\subsection*{Conflicts of Interest}\label{conflicts-of-interest}
\addcontentsline{toc}{subsection}{Conflicts of Interest}

@@

\begin{itemize}
\item
  \textbf{Zhian N. Kamvar} analyzed the data, contributed analysis
  tools, wrote the paper, prepared figures and tables, edited and
  reviewed drafts of the paper.
\item
  \textbf{Bimal Sajeewa Amaradasa} analyzed the data, contributed
  analysis tools, wrote drafts of the paper, edited and reviewed drafts
  of the paper.
\item
  \textbf{Rachana Jhala} Carried out experiments (MCG assessment,
  aggressiveness ratings, genotyping), edited and reviewed drafts of the
  paper.
\item
  \textbf{Serena McCoy} Carried out experiments (MCG assessment,
  aggressiveness ratings, genotyping), edited and reviewed drafts of the
  paper.
\item
  \textbf{James R. Steadman} Conceived and designed experiments,
  organized network of white mold screening nurseries, provided \emph{S.
  sclerotiorum} isolates, edited and reviewed drafts of the paper.
\item
  \textbf{Sydney E. Everhart} supervised data analysis, analyzed the
  data, contributed analysis tools, wrote the paper, edited and reviewed
  drafts of the paper.
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics[width=1.00000\textwidth]{images/mcg-trimmed.png}
\caption{Example of MCG test plates showing (A) a compatible reaction
with mycelia from two strains overgrowing each other and (B) an
incompatible reaction with a barrage line of dead tissue forming between
the two strains. Photo Credit: Rebecca Higgins.}\label{mcg-fig}
\end{figure}
